Concurrent Programming with CXL

### 2020-07-03 book/paper.tex
Latest

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveLock.png}
\caption{The \href{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveLock.html}{HTML output of running CXL on Figure~\ref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The \href{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveFlags.html}{HTML output of running CXL on Figure~\ref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveLock.png}
\caption{The \cxlref{naiveLock.html}{HTML output of running CXL on Figure~\ref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The \cxlref{naiveFlags.html}{HTML output of running CXL on Figure~\ref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}
